\documentclass[11pt,a4paper]{article}

% --------------------
% PACKAGES
% --------------------
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{titlesec}

\geometry{margin=2cm}
\setlength{\parindent}{0pt}

% --------------------
% STYLE
% --------------------
\definecolor{sectioncolor}{RGB}{40,40,40}

\titleformat{\section}
  {\large\bfseries\color{sectioncolor}}
  {}
  {0pt}
  {}

\renewcommand{\labelitemi}{--}

% --------------------
% DOCUMENT
% --------------------
\begin{document}

% --------------------
% HEADER
% --------------------
\begin{center}
    {\LARGE \textbf{JAVIER JOSÉ LOBATO CEBALLOS}}\\
    \vspace{2mm}
    \textbf{Electronics Engineer}\\
    \vspace{2mm}
    \href{mailto:javierlobato@hotmail.com}{javierlobato@hotmail.com} \,|\, 
    +57 300 127 6123 \,|\, ID: 1004360307 \,|\, https://github.com/lob117
\end{center}

\vspace{4mm}
% --------------------
% PROFESSIONAL PROFILE
% --------------------
\section*{Professional Profile}

Electronics Engineer focused on process automation, Digital Innovation, data analysis, and IoT technologies.
Experience in developing Artificial Intelligence-based solutions (OCR and geoparsing),
integration of automated workflows using \textbf{n8n} and \textbf{Docker} containers.
Skilled in managing \textbf{SQL} databases and programming languages such as \textbf{Python and C},
applied to strategic decision-making, operational metrics capture, and process optimization under agile methodologies.

% --------------------
% SKILLS
% --------------------
\section*{Technical Skills}

\begin{itemize}[leftmargin=*]
    \item \textbf{Automation Ecosystem:} Workflow design in n8n and Power Automate.
    \item \textbf{Data Architecture & AI:} SQL database management, implementation of RAG models (Ollama/LangChain), and deployment using Docker containers.
    \item \textbf{Innovation & Prototyping:} Rapid Proof of Concept (PoC) development and IoT hardware integration (ESP32 and STM32) with AWS broker.
    \item \textbf{Process & Data Analysis:} Identification of improvement opportunities, technical requirements gathering, agile methodologies (Scrum), and technical reporting (Excel and Google Sheets).
    \item \textbf{Programming Languages:} Python, C/C++, and SQL.
\end{itemize}

% --------------------
% EXPERIENCE
% --------------------
\section*{Professional Experience}

\textbf{NaturalSIG Corporation} \\
\textit{Electronics Engineer & Process Automation} \hfill August 2025 -- December 2025

\begin{itemize}[leftmargin=*]
    \item Led the \textbf{ideation and design of automation solutions} using OCR and Geoparsing, establishing digital data governance.
    \item Designed the functional architecture of workflows in \textbf{n8n and Docker}, integrating AI components to transform unstructured data into strategic information.
    \item Developed rapid prototypes (\textbf{PoC}) to validate the technical feasibility of integrations between GIS platforms and SQL databases.
\end{itemize}

\vspace{2mm}

\textbf{NaturalSIG Corporation} \\
\textit{UAV Data & Geospatial Workflow Specialist} \hfill January 2025 -- June 2025

\begin{itemize}[leftmargin=*]
    \item Technical management and preventive maintenance of UAV platforms (EbeeX and Phantom 4).
    \item Automated the capture and processing of large datasets from multispectral sensors, optimizing the delivery workflow of 3D models and RGB mosaics.
    \item Ensured the \textbf{integrity of UAV performance metrics} by managing preventive maintenance based on operational data analysis.
\end{itemize}

\vspace{2mm}

\textbf{NaturalSIG Corporation} \\
\textit{Engineering Intern (Optimization & Computer Vision)} \hfill August 2024 -- December 2024

\begin{itemize}[leftmargin=*]
    \item Developed computer vision algorithms for automated vehicle counting, transforming video captures into traffic analysis dashboards.
    \item Designed electrical line structures and buildings in AutoCAD.
\end{itemize}

% --------------------
% EDUCATION
% --------------------
\section*{Education & Certifications}

\textbf{Bachelor’s Degree in Electronics Engineering} \\
Universidad del Magdalena \hfill 2020 -- 2025

\textbf{Certified Drone Pilot (RAC 100):} APD (License: 2449033). \\
APD \hfill 2025

\textbf{Conversational English (B1)} \\
IFT Cajamag \hfill 2025 -- 2026

% --------------------
% ADDITIONAL INFORMATION
% --------------------
\section*{Additional Information}

\textbf{Languages:} English B1 (Conversational). \\
\textbf{Professional License:} AT206-188296. \\
\textbf{Tools:} Git/GitHub, VS Code, WSL2, Linux Environments.

% --------------------
% REFERENCES
% --------------------
\section*{References}

\textbf{Jaime Rodríguez Curcio} \\
Environmental Engineer \\
\href{mailto:ing.ambiental1@naturalsig.org}{ing.ambiental1@naturalsig.org} \\
Phone: 302 408 6564

\vspace{2mm}

\textbf{Gustavo Adolfo Manjarres Pinzón} \\
Biologist \\
\href{mailto:director@naturalsig.org}{director@naturalsig.org} \\
Phone: 321 772 1052

\end{document}